\section{Purpose of the controller}

\hspace{10mm}A passive component designed to resist changes in current. Inductors are often referred to as “AC resistors”. The ability
to resist changes in current and store energy in its magnetic field account for the bulk of the useful properties of inductors. Current passing through an inductor will produce a magnetic field. A changing magnetic field induces a voltage which opposes the field-producing current. This property of impeding changes of current is known as inductance. The voltage induced across an inductor by a change of current is defined as:
$$V = L \frac{di}{dt}$$



\section{Features}


%\hspace{10mm}The DDR3 controller supports the following features: \begin{abstract}
 %   Supports JEDEC standard JESD79-3C – DDR3 compliant devices
%\end{abstract}


\begin{itemize}
    \item 33-bit address for 8 GB of address space.
    \item 16/32/64-bit data bus width support.
    \item CAS latencies: 5, 6, 7, 8, 9, 10, and 11.
    \item 1, 2, 4, and 8 internal banks.
    \item Burst Length: 8.
    \item Burst Type: sequential.
    \item 8GB address space available over one or two chip selects.
    \item Page sizes: 256, 512, 1024, and 2048-word.
    \item SDRAM auto initialization from reset or configuration change.
    \item Self-refresh mode.
    \item Prioritized refresh scheduling.
    \item Programmable SDRAM refresh rate and backlog counter.
    \item Programmable SDRAM timing parameters.
    \item Big and little endian modes.
    \item ECC on SDRAM data bus.
    \item 8-bit ECC per 64-bit data quanta without additional cycle latency.
    \item Two latency classes supported.
    \item UDIMM Address mirroring is not supported.
\end{itemize}
 

\section{The DDR5 technology}
\begin{enumerate}
    \item Every command between the controller and the request must be in bursts (16 (columns or normal requests)).
    \item There is small timing constrains between the commands in different bank groups.
    \item The timing constrains between the two commands in the same bank is the largest then the two banks in the same bank group then the different bank groups.
    \item There is timing constrains between writing to the memory and reading from it.
\end{enumerate}